The K2 Bright Star Survey

### 2019-05-31 paper/ms.tex
misc

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, since these both represent sums of 6\,s exposures \citep{Gilliland2010}. For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star. Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{Kolenberg2011,2013MNRAS.433.1262W,Guzik2016}. In the nominal \kepler mission this was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were assigned short-cadence halo apertures. For these targets we have provided both long- and short-cadence reductions. Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and on choice of objective function, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo light curves.

@@

\begin{figure*}
\plotone{eta_cnc_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the red giant $\eta$~Cancri, in the same format as Figure~\ref{fig:rholeo}. Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$ and $\Dnu = 2.7 \pm 0.03$.}
\label{fig:etacnc}
\end{figure*}

% RGs, Classical pulsators 
\subsection{Classical Variables}
\label{sec:variables}
\textcolor{red}{Variability catalog?}

@@

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star with a period of 1.74\,d. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars.

>>>>

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, since these both represent sums of 6\,s exposures \citep{Gilliland2010}. For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star. Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit t, for various types of variables. Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2013MNRAS.433.1262W} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}.

of the $V = 6$ 16~Cyg~AB, $V=4.48$ $\theta$~Cyg, and the $V=7.2$ RR~Lyr \citep[e.g.][]{,}. In the nominal \kepler mission this was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were assigned short-cadence halo apertures. For these targets we have provided both long- and short-cadence reductions. Following the analysis in Section~\ref{method} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$\,cad and to $k \in {1,2}$, and for consistency with long cadence, we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their many time samples, the short-cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo light curves.

@@

\begin{figure*}
\plotone{eta_cnc_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the red giant $\eta$~Cancri, in the same format as Figure~\ref{fig:rholeo}. Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$\,\muHz and $\Dnu = 2.7 \pm 0.03$\,\muHz.}
\label{fig:etacnc}
\end{figure*}

% RGs, Classical pulsators 
\subsection{Pulsators with Self-Driven Modes}
\label{sec:variables}
\textcolor{red}{Variability catalog?}

@@

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely $\alpha$\,Vir (Spica), interferometry of the Hyades giants, and main-sequence stars with self-driven nonradial modes.
